---
git---
toc: true
toc-depth: 3
title: "Mixed model analysis - summary (IDEAL ILLUMINANT)"
format: html
editor: visual
---

Open .RData file "new_data.RData"

```{r}
load("../data.RData")
```

# Mixed models analysis

```{r}
#| echo: false
#| output: false

#load libraries
library(gapminder)
library(emmeans)
library(scales)
library(stargazer)
library(pavo)
library(readr)
library(dplyr)
library(lme4)
library(nlme)
library(lmerTest)
library(afex)
library(multcomp)
library(mapproj)
library(ggplot2)
library(patchwork)
library(modelsummary)
library(ggpubr)


```

```{r}
#load("../data.RData")

#add new variable TypeAge
TCS_IDEAL_data <- TCS_IDEAL_data %>%
  mutate(TypeAge = paste0(Type, Age))
#scale S9
TCS_IDEAL_data <- TCS_IDEAL_data %>%

  mutate(h.theta_s = scale(h.theta),
         h.phi_s = scale(h.phi),
         r.achieved_s = scale(r.achieved),
         B1_s = scale(B1), 
         H4_s = scale(H4),
         S9_s = scale(S9), 
         S5_s = scale(S5),
         lum_s = scale(lum),
         Tarsus_s = scale(Tarsus),
         Mass_s = scale(Mass),
         Head_s = scale(Head),
         Wing_s= scale(Wing))         
                             
```

mi - (m)odel (i)ncludes ideal illuminant

Dependent variables in models:

mi1 - h.theta_s\
mi2 - h.phi_s\
mi3 - r.achieved_s\
mi4 - lum_s\
mi5 - S9_s\

```{r}

TCS_IDEAL_data$Individual <- as.factor(TCS_IDEAL_data$Individual)
TCS_IDEAL_data$Type <- as.factor(TCS_IDEAL_data$Type)
TCS_IDEAL_data$Nestbox <- as.factor(TCS_IDEAL_data$Nestbox)
TCS_IDEAL_data$Age <- as.factor(TCS_IDEAL_data$Age)
TCS_IDEAL_data$Region <- as.factor(TCS_IDEAL_data$Region)
TCS_IDEAL_data$TypeAge <- as.factor(TCS_IDEAL_data$TypeAge)
```

```{r}
TCS_IDEAL_data.side <- subset(TCS_IDEAL_data, Region == "Side")
TCS_IDEAL_data.maxi <- subset(TCS_IDEAL_data, Region == "Maxilla")
TCS_IDEAL_data.mand <- subset(TCS_IDEAL_data, Region == "Mandible")
TCS_IDEAL_data.pala <- subset(TCS_IDEAL_data, Region == "Palate")
```

# Mi1 - h.theta_s - hue

## Nestlings sex effect (no change compared to model without sex)

```{r}
#| echo: false
#| output: false

TCS_IDEAL_data.maxi$Type <- relevel(TCS_IDEAL_data.maxi$Type, ref = "Dark")
TCS_IDEAL_data.pala$Type <- relevel(TCS_IDEAL_data.pala$Type, ref = "Dark")
TCS_IDEAL_data.side$Type <- relevel(TCS_IDEAL_data.side$Type, ref = "Dark")
TCS_IDEAL_data.mand$Type <- relevel(TCS_IDEAL_data.mand$Type, ref = "Dark")

mi1.side.sex <- lmer(h.theta_s ~ (Type * Age) + Sex + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.side)
mi1.maxi.sex <- lmer(h.theta_s ~ (Type * Age) + Sex + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.maxi)
mi1.mand.sex <- lmer(h.theta_s ~ (Type * Age) + Sex + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.mand)
mi1.pala.sex <- lmer(h.theta_s ~ (Type * Age) + Sex + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.pala)

class(mi1.side.sex) <- "lmerMod"
class(mi1.maxi.sex) <- "lmerMod"
class(mi1.mand.sex) <- "lmerMod"
class(mi1.pala.sex) <- "lmerMod"


h.theta_s.sum.sex <- stargazer(mi1.side.sex, mi1.maxi.sex, mi1.mand.sex, mi1.pala.sex, digits = 2, type = "text", style = "default", title = "h.theta_s Mixed models (Estimate + (Std. Error)", column.labels = c("Flanges", "Maxilla", "Mandible", "Palate"))

```

```{r}

modelsummary(list(mi1.side, mi1.maxi, mi1.mand, mi1.pala),
             statistic = NULL,
             estimate  = "{estimate} [{std.error}]")

```

## Without sex effect

```{r}
#| echo: false
#| output: false

TCS_IDEAL_data.maxi$Type <- relevel(TCS_IDEAL_data.maxi$Type, ref = "Dark")
TCS_IDEAL_data.pala$Type <- relevel(TCS_IDEAL_data.pala$Type, ref = "Dark")
TCS_IDEAL_data.side$Type <- relevel(TCS_IDEAL_data.side$Type, ref = "Dark")
TCS_IDEAL_data.mand$Type <- relevel(TCS_IDEAL_data.mand$Type, ref = "Dark")

mi1.side <- lmer(h.theta_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.side)
mi1.maxi <- lmer(h.theta_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.maxi)
mi1.mand <- lmer(h.theta_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.mand)
mi1.pala <- lmer(h.theta_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.pala)

class(mi1.side) <- "lmerMod"
class(mi1.maxi) <- "lmerMod"
class(mi1.mand) <- "lmerMod"
class(mi1.pala) <- "lmerMod"

h.theta_s.sum <- stargazer(mi1.side, mi1.maxi, mi1.mand, mi1.pala, digits = 2, type = "text", style = "default", title = "h.theta_s Mixed models (Estimate + (Std. Error)", column.labels = c("Flanges", "Maxilla", "Mandible", "Palate"))
```

```{r}
#| echo: false
h.theta_s.sum <- stargazer(mi1.side, mi1.maxi, mi1.mand, mi1.pala, digits = 2, type = "text", style = "default", title = "h.theta_s Mixed models (Estimate + (Std. Error)", column.labels = c("Flanges", "Maxilla", "Mandible", "Palate"))
```

## Graphs

### Side revised

```{r}
summary(mi1.side)
mi1.side.TypeAge <-lmer(h.theta_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.side)
mi1.side.EM <- emmeans(mi1.side.TypeAge, ~TypeAge)


plot.mi1.side <- plot(mi1.side.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans h.theta_s Side", plotit = F)

head(plot.mi1.side) #sprawdzic kolejnosc grup w tabeli i dopisac zmienna z etykeita dla kolorou i linii laczacej grupy

plot.mi1.side$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mi1.side$group <- c("BF", "DF", "DF" ,"BF")
plot.mi1.side$group1 <- c("A1", "A2", "A1" ,"A2")
plot.mi1.side$type <- c("Bright", "Bright", "Dark" ,"Dark")


psidetheta <- ggplot(plot.mi1.side, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  ggtitle("Flanges") + 
  geom_hline(yintercept = plot.mi1.side[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group), color = "black") + 
  geom_point(size = 4)+
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none") +
  ylab ("Hue") + xlab("Group")  +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12" , "Bright\nAge:12"))
  
psidetheta


mi1.side.contr <- contrast(mi1.side.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mi1.side.contr) ##output z CI

```

### Maxilla - revised

```{r}
summary(mi1.maxi)
mi1.maxi.TypeAge <-lmer(h.theta_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.maxi)
mi1.maxi.EM <- emmeans(mi1.maxi.TypeAge, ~TypeAge)

plot.mi1.maxi <- plot(mi1.maxi.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans h.theta_s Maxilla", plotit = F)

head(plot.mi1.maxi)

plot.mi1.maxi$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mi1.maxi$group <- c("BF", "DF", "DF" ,"BF")
plot.mi1.maxi$group1 <- c("A1", "A2", "A1" ,"A2")


pmaxitheta <- ggplot(plot.mi1.maxi, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  ggtitle("Maxilla") + 
  geom_hline(yintercept = plot.mi1.maxi[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group), color = "black") + 
  geom_point(size = 4)+
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none", axis.title.y = element_blank()) +
  ylab ("h.theta_s") + xlab("Group")  +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12" , "Bright\nAge:12"))

mi1.maxi.contr <- contrast(mi1.maxi.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mi1.maxi.contr) ##output z CI


```

### Mandible - revised

```{r}
summary(mi1.mand)
mi1.mand.TypeAge <-lmer(h.theta_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.mand)
mi1.mand.EM <- emmeans(mi1.mand.TypeAge, ~TypeAge)

plot.mi1.mand <- plot(mi1.mand.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans h.theta_s Mandible", plotit = F)

head(plot.mi1.mand)

plot.mi1.mand$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mi1.mand$group <- c("BF", "DF", "DF" ,"BF")
plot.mi1.mand$group1 <- c("A1", "A2", "A1" ,"A2")

pmandtheta <- ggplot(plot.mi1.mand, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  ggtitle("Mandible") + 
  geom_hline(yintercept = plot.mi1.mand[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group), color = "black") + 
  geom_point(size = 4)+
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
 theme(legend.position = "none", axis.title.y = element_blank()) +
  ylab ("h.theta_s") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))


mi1.mand.contr <- contrast(mi1.mand.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mi1.mand.contr) ##output z CI
```

### Palate - revised

```{r}
summary(mi1.pala)
mi1.pala.TypeAge <-lmer(h.theta_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.pala)
mi1.pala.EM <- emmeans(mi1.pala.TypeAge, ~TypeAge)
plot(mi1.pala.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans h.theta_s Palate") + theme_bw() + scale_y_discrete(limits = c("DarkA1", "BrightA1", "DarkA2", "BrightA2"))

plot.mi1.pala <- plot(mi1.pala.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans h.theta_s Palate", plotit = F)

head(plot.mi1.pala)

plot.mi1.pala$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mi1.pala$group <- c("BF", "DF", "DF" ,"BF")
plot.mi1.pala$group1 <- c("A1", "A2", "A1" ,"A2")

ppalatheta <- ggplot(plot.mi1.pala, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  ggtitle("Palate") + 
  geom_hline(yintercept = plot.mi1.pala[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none", axis.title.y = element_blank()) +
  ylab ("h.theta_s") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))



mi1.pala.contr <- contrast(mi1.pala.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 
confint(mi1.pala.contr) ##output z CI
a2 <- psidetheta + pmaxitheta + pmandtheta + ppalatheta
a1 <- psidetheta + pmaxitheta + pmandtheta + ppalatheta
```

# Mi2 - h.phi_s

## Nestlings sex effect (no change compared to the previous model)

```{r}
mi2.side.sex <- lmer(h.phi_s ~ (Type * Age) + Sex + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.side)
mi2.maxi.sex <- lmer(h.phi_s ~ (Type * Age) + Sex + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.maxi)
mi2.mand.sex <- lmer(h.phi_s ~ (Type * Age) + Sex + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.mand)
mi2.pala.sex <- lmer(h.phi_s ~ (Type * Age) + Sex + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.pala)

class(mi2.side.sex) <- "lmerMod"
class(mi2.maxi.sex) <- "lmerMod"
class(mi2.mand.sex) <- "lmerMod"
class(mi2.pala.sex) <- "lmerMod"

h.phi_s.sum.sex <- stargazer(mi2.side.sex, mi2.mand.sex, mi2.maxi.sex, mi2.pala.sex, digits = 2, type = "text", style = "default", title = "h.phi_s Mixed models (Estimate + (Std. Error)", column.labels = c("Side", "Maxilla", "Mandible", "Palate"))

```

## Without sex effect

```{r}
#| echo: false
#| output: false
mi2.side <- lmer(h.phi_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.side)
mi2.maxi <- lmer(h.phi_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.maxi)
mi2.mand <- lmer(h.phi_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.mand)
mi2.pala <- lmer(h.phi_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.pala)

class(mi2.side) <- "lmerMod"
class(mi2.maxi) <- "lmerMod"
class(mi2.mand) <- "lmerMod"
class(mi2.pala) <- "lmerMod"

#| echo: false
h.phi_s.sum <- stargazer(mi2.side, mi2.mand, mi2.maxi, mi2.pala, digits = 2, type = "text", style = "default", title = "h.phi_s Mixed models (Estimate + (Std. Error)", column.labels = c("Side", "Maxilla", "Mandible", "Palate"))
```

## Graphs

### Flanges

```{r}
summary(mi2.side)
mi2.side.TypeAge <-lmer(h.phi_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.side)
mi2.side.EM <- emmeans(mi2.side.TypeAge, ~TypeAge) 

plot.mi2.side <- plot(mi2.side.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans h.phi_s Side", plotit = F)

head(plot.mi2.side)

plot.mi2.side$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mi2.side$group <- c("BF", "DF", "DF" ,"BF")
plot.mi2.side$group1 <- c("A1", "A2", "A1" ,"A2")

psidephi <- ggplot(plot.mi2.side, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.mi2.side[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none") +
  ylab ("Hue") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))



mi2.side.contr <- contrast(mi2.side.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mi2.side.contr) ##output z CI

```

### Maxilla

```{r}
summary(mi2.maxi)
mi2.maxi.TypeAge <-lmer(h.phi_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.maxi)
mi2.maxi.EM <- emmeans(mi2.maxi.TypeAge, ~TypeAge)

plot.mi2.maxi <- plot(mi2.maxi.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans h.phi_s Maxilla", plotit = F)

head(plot.mi2.maxi)

plot.mi2.maxi$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mi2.maxi$group <- c("BF", "DF", "DF" ,"BF")
plot.mi2.maxi$group1 <- c("A1", "A2", "A1" ,"A2")

pmaxiphi <- ggplot(plot.mi2.maxi, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  scale_y_continuous(labels = number_format(accuracy = 0.1)) +
  geom_hline(yintercept = plot.mi2.maxi[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none") +
  ylab ("h.phi_s Maxilla") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))

mi2.maxi.contr <- contrast(mi2.maxi.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mi2.maxi.contr) ##output z CI
```

### Mandible

```{r}
summary(mi2.mand)
mi2.mand.TypeAge <-lmer(h.phi_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.mand)
mi2.mand.EM <- emmeans(mi2.mand.TypeAge, ~TypeAge)

plot.mi2.mand <- plot(mi2.mand.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans h.phi_s Mandible", plotit = F)

head(plot.mi2.mand)

plot.mi2.mand$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mi2.mand$group <- c("BF", "DF", "DF" ,"BF")
plot.mi2.mand$group1 <- c("A1", "A2", "A1" ,"A2")
pmandphi <- ggplot(plot.mi2.mand, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  scale_y_continuous(labels = number_format(accuracy = 0.1)) +
  geom_hline(yintercept = plot.mi2.mand[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none") +
  ylab ("h.phi_s Mandible") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))


mi2.mand.contr <- contrast(mi2.mand.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mi2.mand.contr) ##output z CI
```

### Palate

```{r}
summary(mi2.pala)
mi2.pala.TypeAge <-lmer(h.phi_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.pala)
mi2.pala.EM <- emmeans(mi2.pala.TypeAge, ~TypeAge)

plot.mi2.pala <- plot(mi2.pala.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans h.phi_s Palate", plotit = F)

head(plot.mi2.pala)

plot.mi2.pala$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mi2.pala$group <- c("BF", "DF", "DF" ,"BF")
plot.mi2.pala$group1 <- c("A1", "A2", "A1" ,"A2")
ppalaphi <- ggplot(plot.mi2.pala, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.mi2.pala[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none") +
  ylab ("h.phi_s Palate") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))

mi2.pala.contr <- contrast(mi2.pala.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 
confint(mi2.pala.contr) ##output z CI

psidephi + pmaxiphi + pmandphi + ppalaphi
```

# Mi3 - r.achieved_s

## Nestlings sex effect (no change compared to model without sex)

```{r}
mi3.side.sex <- lmer(r.achieved_s ~ (Type * Age) + Sex + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.side)
mi3.maxi.sex <- lmer(r.achieved_s ~ (Type * Age) + Sex  + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.maxi)
mi3.mand.sex <- lmer(r.achieved_s ~ (Type * Age) + Sex  + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.mand)
mi3.pala.sex <- lmer(r.achieved_s ~ (Type * Age) + Sex  + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.pala)

class(mi3.side.sex) <- "lmerMod"
class(mi3.maxi.sex) <- "lmerMod"
class(mi3.mand.sex) <- "lmerMod"
class(mi3.pala.sex) <- "lmerMod"

r.achieved_s.sum.sex <- stargazer(mi3.side.sex, mi3.maxi.sex, mi3.mand.sex, mi3.pala.sex, digits = 2, type = "text", style = "default", title = "r.achieved_s Mixed models (Estimate + (Std. Error)", column.labels = c("Side", "Maxilla", "Mandible", "Palate"))

```

## Without sex effect

```{r}
#| echo: false
#| output: false
mi3.side <- lmer(r.achieved_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.side)
mi3.maxi <- lmer(r.achieved_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.maxi)
mi3.mand <- lmer(r.achieved_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.mand)
mi3.pala <- lmer(r.achieved_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.pala)

class(mi3.side) <- "lmerMod"
class(mi3.maxi) <- "lmerMod"
class(mi3.mand) <- "lmerMod"
class(mi3.pala) <- "lmerMod"

r.achieved_s.sum <- stargazer(mi3.side, mi3.maxi, mi3.mand, mi3.pala, digits = 2, type = "text", style = "default", title = "r.achieved_s Mixed models (Estimate + (Std. Error)", column.labels = c("Side", "Maxilla", "Mandible", "Palate"))
```

### Flanges

```{r}
summary(mi3.side)
mi3.side.TypeAge <-lmer(r.achieved_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.side)
mi3.side.EM <- emmeans(mi3.side.TypeAge, ~TypeAge)

plot.mi3.side <- plot(mi3.side.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans r.achieved_s Side", plotit = F)

head(plot.mi3.side)

plot.mi3.side$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mi3.side$group <- c("BF", "DF", "DF" ,"BF")
plot.mi3.side$group1 <- c("A1", "A2", "A1" ,"A2")
psideach <- ggplot(plot.mi3.side, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  scale_y_continuous(labels = number_format(accuracy = 0.1)) +
  geom_hline(yintercept = plot.mi3.side[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none") +
  ylab ("r.achieved_s Side") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))


mi3.side.contr <- contrast(mi3.side.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mi3.side.contr) ##output z CI

```

### Maxilla

```{r}
summary(mi3.maxi)
mi3.maxi.TypeAge <-lmer(r.achieved_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.maxi)
mi3.maxi.EM <- emmeans(mi3.maxi.TypeAge, ~TypeAge)

plot.mi3.maxi <- plot(mi3.maxi.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans r.achieved_s Maxilla", plotit = F)

head(plot.mi3.maxi)

plot.mi3.maxi$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mi3.maxi$group <- c("BF", "DF", "DF" ,"BF")
plot.mi3.maxi$group1 <- c("A1", "A2", "A1" ,"A2")
pmaxiach <- ggplot(plot.mi3.maxi, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.mi3.maxi[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none") +
  ylab ("r.achieved_s Maxilla") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))



mi3.maxi.contr <- contrast(mi3.maxi.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mi3.maxi.contr) ##output z CI
```

### Mandible

```{r}
summary(mi3.mand)
mi3.mand.TypeAge <-lmer(r.achieved_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.mand)
mi3.mand.EM <- emmeans(mi3.mand.TypeAge, ~TypeAge)
plot.mi3.mand <- plot(mi3.mand.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans r.achieved_s Mandible", plotit = F)

head(plot.mi3.mand)

plot.mi3.mand$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mi3.mand$group <- c("BF", "DF", "DF" ,"BF")
plot.mi3.mand$group1 <- c("A1", "A2", "A1" ,"A2")
pmandach <- ggplot(plot.mi3.mand, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.mi3.mand[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none") +
  ylab ("r.achieved_s Mandible") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))

mi3.mand.contr <- contrast(mi3.mand.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mi3.mand.contr) ##output z CI
```

### Palate

```{r}
summary(mi3.pala)
mi3.pala.TypeAge <-lmer(r.achieved_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.pala)
mi3.pala.EM <- emmeans(mi3.pala.TypeAge, ~TypeAge)

plot.mi3.pala <- plot(mi3.pala.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans r.achieved_s Palate", plotit = F)

head(plot.mi3.pala)

plot.mi3.pala$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mi3.pala$group <- c("BF", "DF", "DF" ,"BF")
plot.mi3.pala$group1 <- c("A1", "A2", "A1" ,"A2")
ppalaach <- ggplot(plot.mi3.pala, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  scale_y_continuous(labels = number_format(accuracy = 0.1)) +
  geom_hline(yintercept = plot.mi3.pala[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none") +
  ylab ("r.achieved_s Palate") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))

mi3.pala.contr <- contrast(mi3.pala.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 
confint(mi3.pala.contr) ##output z CI

psideach + pmaxiach + pmandach + ppalaach
```

# Mi4 - lum_s - luminance

## Nestlings sex effect (no change compared to model without sex)

```{r}
TCS_IDEAL_data.maxi$Type <- relevel(TCS_IDEAL_data.maxi$Type, ref = "Dark")
TCS_IDEAL_data.pala$Type <- relevel(TCS_IDEAL_data.pala$Type, ref = "Dark")
TCS_IDEAL_data.side$Type <- relevel(TCS_IDEAL_data.side$Type, ref = "Dark")
TCS_IDEAL_data.mand$Type <- relevel(TCS_IDEAL_data.mand$Type, ref = "Dark")

mi4.side.sex <- lmer(lum_s ~ (Type * Age) + Sex + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.side)
mi4.maxi.sex <- lmer(lum_s ~ (Type * Age) + Sex + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.maxi)
mi4.mand.sex <- lmer(lum_s ~ (Type * Age) + Sex + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.mand)
mi4.pala.sex <- lmer(lum_s ~ (Type * Age) + Sex + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.pala)

class(mi4.side.sex) <- "lmerMod"
class(mi4.maxi.sex) <- "lmerMod"
class(mi4.mand.sex) <- "lmerMod"
class(mi4.pala.sex) <- "lmerMod"

lum_s.sum.sex <- stargazer(mi4.side.sex, mi4.maxi.sex, mi4.mand.sex, mi4.pala.sex, digits = 2, type = "text", style = "default", title = "lum_s Mixed models (Estimate + (Std. Error)", column.labels = c("Side", "Maxilla", "Mandible", "Palate"))
```

## Without sex effect

```{r}
#| echo: false
#| output: false

TCS_IDEAL_data.maxi$Type <- relevel(TCS_IDEAL_data.maxi$Type, ref = "Dark")
TCS_IDEAL_data.pala$Type <- relevel(TCS_IDEAL_data.pala$Type, ref = "Dark")
TCS_IDEAL_data.side$Type <- relevel(TCS_IDEAL_data.side$Type, ref = "Dark")
TCS_IDEAL_data.mand$Type <- relevel(TCS_IDEAL_data.mand$Type, ref = "Dark")

mi4.side <- lmer(lum_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.side)
mi4.maxi <- lmer(lum_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.maxi)
mi4.mand <- lmer(lum_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.mand)
mi4.pala <- lmer(lum_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.pala)

class(mi4.side) <- "lmerMod"
class(mi4.maxi) <- "lmerMod"
class(mi4.mand) <- "lmerMod"
class(mi4.pala) <- "lmerMod"

lum_s.sum <- stargazer(mi4.side, mi4.maxi, mi4.mand, mi4.pala, digits = 2, type = "text", style = "default", title = "lum_s Mixed models (Estimate + (Std. Error)", column.labels = c("Side", "Maxilla", "Mandible", "Palate"))
```

### Flanges - revised

```{r}
summary(mi4.side)
mi4.side.TypeAge <-lmer(lum_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.side)
mi4.side.EM <- emmeans(mi4.side.TypeAge, ~TypeAge)

plot.mi4.side <- plot(mi4.side.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans lum_s Side", plotit = F)

head(plot.mi4.side)

plot.mi4.side$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mi4.side$group <- c("BF", "DF", "DF" ,"BF")
plot.mi4.side$group1 <- c("A1", "A2", "A1" ,"A2")

psidelum <- ggplot(plot.mi4.side, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.mi4.side[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none") +
  ylab ("Luminance") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))


mi4.side.contr <- contrast(mi4.side.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mi4.side.contr) ##output z CI

```

### Maxilla - revised

```{r}
summary(mi4.maxi)
mi4.maxi.TypeAge <-lmer(lum_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.maxi)
mi4.maxi.EM <- emmeans(mi4.maxi.TypeAge, ~TypeAge)

plot.mi4.maxi <- plot(mi4.maxi.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans lum_s Maxilla", plotit = F)

head(plot.mi4.maxi)

plot.mi4.maxi$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mi4.maxi$group <- c("BF", "DF", "DF" ,"BF")
plot.mi4.maxi$group1 <- c("A1", "A2", "A1" ,"A2")
pmaxilum <- ggplot(plot.mi4.maxi, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.mi4.maxi[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none", axis.title.y = element_blank()) +
  ylab ("lum_s Maxilla") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))



mi4.maxi.contr <- contrast(mi4.maxi.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mi4.maxi.contr) ##output z CI
```

### Mandible - revised

```{r}
summary(mi4.mand)
mi4.mand.TypeAge <-lmer(lum_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.mand)
mi4.mand.EM <- emmeans(mi4.mand.TypeAge, ~TypeAge)

plot.mi4.mand <- plot(mi4.mand.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans lum_s Mandible", plotit = F)

head(plot.mi4.mand)

plot.mi4.mand$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mi4.mand$group <- c("BF", "DF", "DF" ,"BF")
plot.mi4.mand$group1 <- c("A1", "A2", "A1" ,"A2")
pmandlum <- ggplot(plot.mi4.mand, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.mi4.mand[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none", axis.title.y = element_blank()) +
  ylab ("lum_s Mandible") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))



mi4.mand.contr <- contrast(mi4.mand.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mi4.mand.contr) ##output z CI
```

### Palate - revised

```{r}
summary(mi4.pala)
mi4.pala.TypeAge <-lmer(lum_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.pala)
mi4.pala.EM <- emmeans(mi4.pala.TypeAge, ~TypeAge)

plot.mi4.pala <- plot(mi4.pala.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans lum_s Palate", plotit = F)

head(plot.mi4.pala)

plot.mi4.pala$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mi4.pala$group <- c("BF", "DF", "DF" ,"BF")
plot.mi4.pala$group1 <- c("A1", "A2", "A1" ,"A2")
ppalalum <- ggplot(plot.mi4.pala, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.mi4.pala[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none", axis.title.y = element_blank()) +
  ylab ("lum_s Palate") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))


mi4.pala.contr <- contrast(mi4.pala.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 
confint(mi4.pala.contr) ##output z CI

psidelum + pmaxilum + pmandlum + ppalalum
```

# Mi5 - S9_s

## Nestlings sex effect (no change compared to model without sex)

```{r}
#| echo: false
#| output: false
mi5.side.sex <- lmer(S9_s ~ (Type * Age) + Sex + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.side)
mi5.maxi.sex <- lmer(S9_s ~ (Type * Age) + Sex + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.maxi)
mi5.mand.sex <- lmer(S9_s ~ (Type * Age) + Sex + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.mand)
mi5.pala.sex <- lmer(S9_s ~ (Type * Age) + Sex + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.pala)

class(mi5.side.sex) <- "lmerMod"
class(mi5.maxi.sex) <- "lmerMod"
class(mi5.mand.sex) <- "lmerMod"
class(mi5.pala.sex) <- "lmerMod"

S9_s.sum.sex<- stargazer(mi5.side.sex, mi5.maxi.sex, mi5.mand.sex, mi5.pala.sex, digits = 2, type = "text", style = "default", title = "S9_s Mixed models (Estimate + (Std. Error)", column.labels = c("Side", "Maxilla", "Mandible", "Palate"))
```

## Without sex effect

```{r}
#| echo: false
#| output: false
mi5.side <- lmer(S9_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.side)
mi5.maxi <- lmer(S9_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.maxi)
mi5.mand <- lmer(S9_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.mand)
mi5.pala <- lmer(S9_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.pala)

class(mi5.side) <- "lmerMod"
class(mi5.maxi) <- "lmerMod"
class(mi5.mand) <- "lmerMod"
class(mi5.pala) <- "lmerMod"

S9_s.sum <- stargazer(mi5.side, mi5.maxi, mi5.mand, mi5.pala, digits = 2,
                      type = "text", style = "default", title = "S9_s Mixed models (Estimate + (Std. Error)", column.labels = c("Side", "Maxilla", "Mandible", "Palate"))
```

### Flanges - revised

```{r}
summary(mi5.side)
mi5.side.TypeAge <-lmer(S9_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.side)
mi5.side.EM <- emmeans(mi5.side.TypeAge, ~TypeAge)

plot.mi5.side <- plot(mi5.side.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans S9 Side", plotit = F)

head(plot.mi5.side)

plot.mi5.side$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mi5.side$group <- c("BF", "DF", "DF" ,"BF")
plot.mi5.side$group1 <- c("A1", "A2", "A1" ,"A2")

psideS9 <- ggplot(plot.mi5.side, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  scale_y_continuous(labels = number_format(accuracy = 0.1)) +
  geom_hline(yintercept = plot.mi5.side[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none") +
  ylab ("Carotenoid chroma") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))

mi5.side.contr <- contrast(mi5.side.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mi5.side.contr) ##output z CI

```

### Maxilla - revised

```{r}
summary(mi5.maxi)
mi5.maxi.TypeAge <-lmer(S9_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.maxi)
mi5.maxi.EM <- emmeans(mi5.maxi.TypeAge, ~TypeAge)

plot.mi5.maxi <- plot(mi5.maxi.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans S9 Maxilla", plotit = F)

head(plot.mi5.maxi)

plot.mi5.maxi$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mi5.maxi$group <- c("BF", "DF", "DF" ,"BF")
plot.mi5.maxi$group1 <- c("A1", "A2", "A1" ,"A2")

pmaxiS9 <- ggplot(plot.mi5.maxi, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.mi5.maxi[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none", axis.title.y = element_blank()) +
  ylab ("S9 Maxilla") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))


mi5.maxi.contr <- contrast(mi5.maxi.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mi5.maxi.contr) ##output z CI
```

### Mandible - revised

```{r}
summary(mi5.mand)
mi5.mand.TypeAge <-lmer(S9_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.mand)
mi5.mand.EM <- emmeans(mi5.mand.TypeAge, ~TypeAge)


plot.mi5.mand <- plot(mi5.mand.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans S9 Mandible", plotit = F)

head(plot.mi5.mand)

plot.mi5.mand$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mi5.mand$group <- c("BF", "DF", "DF" ,"BF")
plot.mi5.mand$group1 <- c("A1", "A2", "A1" ,"A2")

pmandS9 <- ggplot(plot.mi5.mand, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.mi5.mand[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
   theme(legend.position = "none", axis.title.y = element_blank()) +
  ylab ("S9 Mandible") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))

mi5.mand.contr <- contrast(mi5.mand.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mi5.mand.contr) ##output z CI
```

### Palate - revised

```{r}
summary(mi5.pala)
mi5.pala.TypeAge <-lmer(S9_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.pala)
mi5.pala.EM <- emmeans(mi5.pala.TypeAge, ~TypeAge)

plot.mi5.pala <- plot(mi5.pala.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans S9 Palate", plotit = F)

head(plot.mi5.pala)

plot.mi5.pala$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mi5.pala$group <- c("BF", "DF", "DF" ,"BF")
plot.mi5.pala$group1 <- c("A1", "A2", "A1" ,"A2")

ppalaS9 <- ggplot(plot.mi5.pala, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.mi5.pala[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none", axis.title.y = element_blank()) +
  ylab ("S9 Palate") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))


mi5.pala.contr <- contrast(mi5.pala.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 
confint(mi5.pala.contr) ##output z CI

psideS9 + pmaxiS9 + pmandS9 + ppalaS9
```

# PATCHWORK

```{r}

My_Theme = theme(
  axis.title.x = element_blank(),
  axis.text.x = element_blank(),
  axis.text.y = element_text(size = 8),
  axis.title.y = element_text(size = 10)) + 
  theme(axis.text.y = element_text(colour = "black")) + theme_bw() + theme_update(plot.title = element_text(hjust = 0.5), legend.position = "none") 

My_Theme_S9 = theme(
  axis.title.x = element_blank(),
  axis.text.x = element_text(size = 8),
  axis.text.y = element_text(size = 8),
  axis.title.y = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black"), axis.text.y = element_text(colour = "black")) + theme_bw() + theme_update(plot.title = element_text(hjust = 0.5),legend.position = "none")
```

Revised Graph3 patchwork

```{r}
pi.theta <- (psidetheta | pmaxitheta | pmandtheta | ppalatheta) & My_Theme
pi.theta <- pi.theta & labs(y = 'Hue', x= '')
pi.theta <- pi.theta + plot_layout(axes = "collect")
pi.theta <- pi.theta + plot_layout(axes = "collect")
pi.theta <- pi.theta & My_Theme

pi.lum <- (psidelum | pmaxilum | pmandlum | ppalalum) & My_Theme 
pi.lum <- pi.lum & labs(y= 'Luminance', x= '')
pi.lum <- pi.lum + plot_layout(axes = "collect")
pi.lum

pi.S9 <- (psideS9 | pmaxiS9 | pmandS9 | ppalaS9) & My_Theme_S9
pi.S9 <- pi.S9 & labs(y= 'Carotenoid chroma', x= '')
pi.S9 <- pi.S9 + plot_layout(axes = "collect")
pi.S9

ideal_patchwork <- pi.theta /pi.lum / pi.S9
id_p <- ideal_patchwork & theme(axis.text.x = element_blank())
id_p + theme_bw() + theme(legend.position = "none")
```

```{r}
pi.theta <- (psidetheta | pmaxitheta | pmandtheta | ppalatheta) & My_Theme
pi.theta <- pi.theta & labs(y = 'h.theta_s', x= '')
pi.theta <- pi.theta + plot_layout(axes = "collect")
pi.theta <- pi.theta + plot_layout(axes = "collect")
pi.theta <- pi.theta & My_Theme

#pi.phi <- (psidephi | pmaxiphi | pmandphi | ppalaphi) & My_Theme 
#pi.phi <- pi.phi & labs(y= 'h.phi_s', x= '')
#pi.phi <- pi.phi + plot_layout(axes = "collect")
#pi.phi

#pi.r.ach <- (psideach | pmaxiach | pmandach | ppalaach) & My_Theme 
#pi.r.ach <- pi.r.ach & labs(y= 'r.achieved_s', x= '')
#pi.r.ach <- pi.r.ach + plot_layout(axes = "collect")
#pi.r.ach

pi.lum <- (psidelum | pmaxilum | pmandlum | ppalalum) & My_Theme 
pi.lum <- pi.lum & labs(y= 'lum_s', x= '')
pi.lum <- pi.lum + plot_layout(axes = "collect")
pi.lum

pi.S9 <- (psideS9 | pmaxiS9 | pmandS9 | ppalaS9) & My_Theme_S9
pi.S9 <- pi.S9 & labs(y= 'S9_s', x= '')
pi.S9 <- pi.S9 + plot_layout(axes = "collect")
pi.S9

ideal_patchwork <- pi.theta/pi.lum / pi.S9
id_p <- ideal_patchwork & theme(axis.text.x = element_blank())
id_p + theme_bw() + theme(legend.position = "none")

```

```{r}
seg1 <- psidetheta + labs(y= 'h.theta_s')


         
seg1
seg1 <- seg1 + plot_layout(axes = "collect")

seg1 <- (psidephi / psidephi / psideach / psidelum/psideS9) & labs(y= 'h.theta_s') 
seg1 <- seg1 + plot_layout(axes = "collect")

seg1 <- (psidetheta / psidephi / psideach / psidelum/psideS9) & labs(y= 'h.theta_s') 
seg1 <- seg1 + plot_layout(axes = "collect")

seg1 <- (psidetheta / psidephi / psideach / psidelum/psideS9) & labs(y= 'h.theta_s') 
seg1 <- seg1 + plot_layout(axes = "collect")



(pmaxitheta/pmaxilum/pmaxiS9)
```

# GGARRANGE

```{r}

grid1 <- ggarrange(psidetheta, pmaxitheta, pmandtheta, ppalatheta,
                   ncol = 4, nrow = 1)

grid2 <- ggarrange(psidelum, pmaxilum, pmandlum, ppalalum,
                   ncol = 4, nrow = 1)

grid3 <- ggarrange(psideS9, pmaxiS9, pmandS9, ppalaS9,
                   ncol = 4, nrow = 1)
  
grid_ideal <- ggarrange(grid1, grid2, grid3,labels = c("A", "B" , "C"),
                        ncol = 1, nrow = 3)  

ggsave(filename = "figure2.pdf", device = "pdf")
       

#real illuminant: 
#grid4 <- ggarrange(rsidetheta, rmaxitheta, rmandtheta, rpalatheta, ncol = 4, nrow = 1)
#grid5 <- ggarrange(rsidelum, rmaxilum, rmandlum, rpalalum, ncol = 4, nrow = 1)      
#grid_real <- ggarrange(grid4, grid5, ncol = 1, nrow = 2, labels = c("A", "B"))
                   
#grid_real

#ggsave(filename = "figure3.pdf", device = "pdf")
        

```

### Morphometric data analysis

```{r}

anov.tarsus <- aov(Tarsus ~ TypeAge, data = TCS_IDEAL_data.side)
TukeyHSD(anov.tarsus)
plot(TukeyHSD(anov.tarsus))
pairwise.t.test(Tarsus ~ TypeAge, data = TCS_IDEAL_data.side, p.adjust.method = "holm")
par(mfrow = c(2,2))
plot(anov.tarsus)

plot(Tarsus ~ TypeAge, data = TCS_IDEAL_data.side) 

anov.mass <- aov(Mass ~ TypeAge, data = TCS_IDEAL_data.side)
TukeyHSD(anov.mass)
plot(anov.mass)
plot(Mass ~ TypeAge, data = TCS_IDEAL_data.side)

anov.head <- aov(Head ~ TypeAge, data = TCS_IDEAL_data.side)
TukeyHSD(anov.head)
plot(anov.head)
plot(Head ~ TypeAge, data = TCS_IDEAL_data.side)

anov.wing <- aov(Wing ~ TypeAge, data = TCS_IDEAL_data.side)
TukeyHSD(anov.wing)
plot(anov.wing)
plot(Wing ~ TypeAge, data = TCS_IDEAL_data.side)



plot(Tarsus ~ TypeAge, data = TCS_IDEAL_data.side) 
plot(Mass ~ TypeAge, data = TCS_IDEAL_data.side)
plot(Head ~ TypeAge, data = TCS_IDEAL_data.side)
plot(Wing ~ TypeAge, data = TCS_IDEAL_data.side)


```

# LMER biometry

## Tarsus

```{r}
model.tarsus <- lmer(Tarsus ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.side)
summary(model.tarsus)
tarsus.TypeAge <-lmer(Tarsus ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.side)
tarsus.EM <- emmeans(tarsus.TypeAge, ~TypeAge)

plot.tarsus <- plot(tarsus.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans Tarsus", plotit = F)

head(plot.tarsus)

plot.tarsus$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.tarsus$group <- c("BF", "DF", "DF" ,"BF")
plot.tarsus$group1 <- c("A1", "A2", "A1" ,"A2")

ptarsus <- ggplot(plot.tarsus, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.tarsus[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none", axis.title.y = element_text())+
  ylab ("Tarsus length") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))


tarsus.contr <- contrast(tarsus.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 
confint(tarsus.contr)
```

## Mass

```{r}
model.mass <- lmer(Mass ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.side)
summary(model.mass)
mass.TypeAge <-lmer(Mass ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.side)
mass.EM <- emmeans(mass.TypeAge, ~TypeAge)

plot.mass <- plot(mass.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans Mass", plotit = F)

head(plot.mass)

plot.mass$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mass$group <- c("BF", "DF", "DF" ,"BF")
plot.mass$group1 <- c("A1", "A2", "A1" ,"A2")

pmass <- ggplot(plot.mass, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.mass[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none", axis.title.y = element_text()) +
  ylab ("Body mass") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))


mass.contr <- contrast(mass.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 
confint(mass.contr)
```

## Head

```{r}
model.head <- lmer(Head ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.side)
summary(model.head)
head.TypeAge <-lmer(Head ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.side)
head.EM <- emmeans(head.TypeAge, ~TypeAge)

plot.head <- plot(head.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans Head", plotit = F)

head(plot.head)

plot.head$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.head$group <- c("BF", "DF", "DF" ,"BF")
plot.head$group1 <- c("A1", "A2", "A1" ,"A2")

phead <- ggplot(plot.head, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.head[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none", axis.title.y = element_text()) +
  ylab ("Head length") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))


head.contr <- contrast(head.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 
confint(head.contr)
```

## Wing

```{r}
model.wing <- lmer(Wing ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.side)
summary(model.wing)

wing.TypeAge <-lmer(Wing ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.side)
wing.EM <- emmeans(wing.TypeAge, ~TypeAge)

plot.wing <- plot(wing.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans Head", plotit = F)

head(plot.wing)

plot.wing$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.wing$group <- c("BF", "DF", "DF" ,"BF")
plot.wing$group1 <- c("A1", "A2", "A1" ,"A2")

pwing <- ggplot(plot.wing, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.wing[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none", axis.title.y = element_text())+
  ylab ("Wing length") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))


wing.contr <- contrast(wing.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 
confint(wing.contr)
```

## Graphs biometry

```{r}


(ptarsus + pmass) / (phead + pwing)


biometry_grid <- ggarrange(ptarsus, pmass, phead, pwing, labels = c("A", "B" , "C", "D"),ncol = 2, nrow = 2)
  
 
```

## Biometry summary

```{r}
class(tarsus.TypeAge) <- "lmerMod"
class(mass.TypeAge) <- "lmerMod"
class(head.TypeAge) <- "lmerMod"
class(wing.TypeAge) <- "lmerMod"

biometr.sum.typeage <- stargazer(tarsus.TypeAge, mass.TypeAge, head.TypeAge, wing.TypeAge, digits = 2, type = "text", style = "default", title = "Biometry Mixed models (Estimate + (Std. Error)")


class(model.tarsus) <- "lmerMod"
class(model.mass) <- "lmerMod"
class(model.head) <- "lmerMod"
class(model.wing) <- "lmerMod"

biometr.sum <- stargazer(model.tarsus, model.mass, model.head, model.wing, digits = 2, type = "text", style = "default", title = "Biometry Mixed models (Estimate + (Std. Error)")
```

# Biometry-color models

## HUE

```{r}

mi1.side.tarsus <- lmer(h.theta_s ~ (Type * Age) + Tarsus_s + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.side)
mi1.maxi.tarsus <- lmer(h.theta_s ~ (Type * Age) + Tarsus_s + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.maxi)
mi1.mand.tarsus <- lmer(h.theta_s ~ (Type * Age) + Tarsus_s + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.mand)
mi1.pala.tarsus <- lmer(h.theta_s ~ (Type * Age) + Tarsus_s + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.pala)

class(mi1.side.tarsus) <- "lmerMod"
class(mi1.maxi.tarsus) <- "lmerMod"
class(mi1.mand.tarsus) <- "lmerMod"
class(mi1.pala.tarsus) <- "lmerMod"


h.theta_s.sum.tarsus <- stargazer(mi1.side.tarsus, mi1.maxi.tarsus, mi1.mand.tarsus, mi1.pala.tarsus, digits = 2, type = "text", style = "default", title = "h.theta_s Mixed models (Estimate + (Std. Error)", column.labels = c("Flanges", "Maxilla", "Mandible", "Palate"))



```

Add interaction term between biometric variable and treatment

```{r}
mi1.side.tarsus.int <- lmer(h.theta_s ~ Age + (Type * Tarsus_s) + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.side)
mi1.maxi.tarsus.int <- lmer(h.theta_s ~ Age + (Type * Tarsus_s) + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.maxi)
mi1.mand.tarsus.int <- lmer(h.theta_s ~ Age + (Type * Tarsus_s) + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.mand)
mi1.pala.tarsus.int <- lmer(h.theta_s ~ Age + (Type * Tarsus_s) + (1|Individual) + (1|Nestbox), data = TCS_IDEAL_data.pala)

class(mi1.side.tarsus.int) <- "lmerMod"
class(mi1.maxi.tarsus.int) <- "lmerMod"
class(mi1.mand.tarsus.int) <- "lmerMod"
class(mi1.pala.tarsus.int) <- "lmerMod"


h.theta_s.sum.tarsus.interaction <- 
stargazer(mi1.side.tarsus.int, mi1.maxi.tarsus.int, mi1.mand.tarsus.int, mi1.pala.tarsus.int, digits = 2, type = "text", style = "default", title = "interaction Mixed models (Estimate + (Std. Error)", column.labels = c("Flanges", "Maxilla", "Mandible", "Palate"))

```
